\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{array}
\usepackage{tabularx}

% PDF metadata
\hypersetup{
    pdftitle={Hamza EL MASSOUDI Resume},
    pdfauthor={Hamza EL MASSOUDI},
    colorlinks=true,
    urlcolor=blue
}

% --------------------------------------------------
% Page layout
% --------------------------------------------------
\geometry{
    top    = 0.5in,
    bottom = 0.5in,
    left   = 0.5in,
    right  = 0.5in
}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\pagenumbering{gobble}

% --------------------------------------------------
% Section formatting
% --------------------------------------------------
\titleformat{\section}{\bfseries\large\raggedright}{}{0pt}{}
\titlespacing*{\section}{0pt}{6pt}{4pt}

% --------------------------------------------------
% Document start
% --------------------------------------------------
\begin{document}

% --------------------------------------------------
% Header
% --------------------------------------------------
\begin{center}
    {\LARGE \textbf{Hamza EL MASSOUDI}}\\
    \smallskip
    Software Engineer \textbar\ Casablanca, Morocco\\
    \smallskip
    \faPhone\; +212 697 56 68 01 \quad
    \href{mailto:hamza.elmassoudi.dev@gmail.com}{hamza.elmassoudi.dev@gmail.com} \quad
    \href{https://www.linkedin.com/in/hamza-el-massoudi-29a558235/}{\faLinkedin\ linkedin.com/in/hamza-el-massoudi-29a558235} \quad
    \href{https://github.com/ygwoah/}{\faGithub\ github.com/ygwoah}
\end{center}
\vspace{-4pt}
\hrule
\vspace{8pt}

% --------------------------------------------------
% Summary
% --------------------------------------------------
\section*{Summary}
Full-stack engineer specialized in distributed search systems (Oracle Cloud Infrastructure). Delivered 35\% faster CI pipelines and robust plugin-test coverage for OpenSearch. Adept at building scalable web/mobile apps and integrating AI-powered solutions using React, Spring Boot, PostgreSQL, and Docker.

% --------------------------------------------------
% Education
% --------------------------------------------------
\section{EDUCATION}

\begin{tabularx}{\linewidth}{@{}p{0.78\linewidth} r@{}}
	\textbf{Engineering Degree, Software Engineering \& Distributed Systems} — Ecole Normale Supérieure de l’Enseignement Technique, Mohammedia & 2022--2025 \\
	\textbf{B.Sc. Mathematics \& Computer Science} — Faculty of Science and Technology, Al Hoceima & 2021--2022 \\
	\textbf{DEUST} (Scientific and Technical University Studies) — Faculty of Science and Technology, Al Hoceima & 2019--2021 \\
\end{tabularx}

% --------------------------------------------------
% Experience
% --------------------------------------------------
\section{EXPERIENCE}

	\textbf{Software Engineer Intern — Oracle, OCI Search with OpenSearch}
\hfill Feb 2025--Aug 2025\\
Casablanca, Morocco
\begin{itemize}[leftmargin=*]
    \item Optimized and automated the CI pipeline (Jenkins, GitHub Actions), reducing test-suite time by 35\%.
    \item Engineered and maintained a robust plugin-test suite (security, performance, regression) for OpenSearch using Python and Bash.
    \item Collaborated with distributed teams to deliver scalable search solutions on Oracle Cloud Infrastructure.
\end{itemize}

	\textbf{Software Engineering Intern — FeverToken}
\hfill Jun 2023--Aug 2023\\
Remote
\begin{itemize}[leftmargin=*]
    \item Developed and deployed a React Native mobile app, integrating Firebase Auth, Expo Push, and real-time data sync.
    \item Led agile ceremonies, conducted code reviews, and accelerated feature delivery by 20\%.
    \item Enhanced user experience for 500+ users by optimizing app performance and reliability.
\end{itemize}

% --------------------------------------------------
% Projects
% --------------------------------------------------
\section{PROJECTS}

	\textbf{Student Engagement \& Academic Management Platform (Freelance -- Contract)}
\hfill Sep 2024--Dec 2024 \\
Freelance
\begin{itemize}[leftmargin=*]
    \item Architected and delivered a scalable React Native app for 1,000+ concurrent students, enabling self-service, community engagement, and mentor matching.
    \item Integrated an AI-powered chatbot to automate and resolve student FAQs instantly.
    \item Engineered the platform using React Native, Node.js/Express, PostgreSQL, and OpenAI API.
\end{itemize}

	\textbf{Survey Creation Platform}
\hfill 2024 \\
Personal Project
\begin{itemize}[leftmargin=*]
    \item Conceived and engineered a full-stack web platform for creating, distributing, and analyzing surveys.
    \item Implemented RESTful APIs and core business logic with \textbf{Spring Boot}, reducing survey creation time by 30\%.
    \item Crafted an intuitive, responsive frontend in \textbf{React} for seamless survey creation and real-time results visualization.
    \item Leveraged \textbf{PostgreSQL} for secure, scalable data management.
    \item Integrated user authentication and dynamic analytics to enhance user experience.
\end{itemize}

% --------------------------------------------------
% Skills
% --------------------------------------------------
\section{SKILLS}

	\textbf{Programming Languages}: TypeScript, JavaScript, Java \\
	\textbf{Frontend}: React, React Native, Next.js, Tailwind CSS \\
	\textbf{Backend}: Spring Boot, Express.js, Node.js \\
	\textbf{Databases}: MySQL, PostgreSQL, MongoDB, Firestore \\
	\textbf{DevOps \& Cloud}: Docker, Git, Linux, OCI, Terraform \\
	\textbf{Infrastructure-as-Code \& Orchestration}: Kubernetes

% --------------------------------------------------
% Languages & Interests
% --------------------------------------------------
\section{LANGUAGES \& INTERESTS}

	\textbf{Languages}: Arabic (Native), English (Fluent), French (Fluent) \\
	\textbf{Interests}: Football, Reading, Competitive Programming

\end{document}