\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{array}
\usepackage{tabularx}

% PDF metadata
\hypersetup{
    pdftitle={Hamza EL MASSOUDI Resume},
    pdfauthor={Hamza EL MASSOUDI},
    colorlinks=true,
    urlcolor=blue
}

% --------------------------------------------------
% Page layout
% --------------------------------------------------
\geometry{
    top    = 0.5in,
    bottom = 0.5in,
    left   = 0.5in,
    right  = 0.5in
}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\pagenumbering{gobble}

% --------------------------------------------------
% Section formatting
% --------------------------------------------------
\titleformat{\section}{\bfseries\large\raggedright}{}{0pt}{}
\titlespacing*{\section}{0pt}{6pt}{4pt}

% --------------------------------------------------
% Document start
% --------------------------------------------------
\begin{document}

% --------------------------------------------------
% Header
% --------------------------------------------------
\begin{center}
    {\LARGE \textbf{Hamza EL MASSOUDI}}\\
    \smallskip
    Software Engineer \textbar\ Casablanca, Morocco\\
    \smallskip
    \faPhone\; +212 697 56 68 01 \quad
    \href{mailto:hamza.elmassoudi.dev@gmail.com}{hamza.elmassoudi.dev@gmail.com} \quad
    \href{https://www.linkedin.com/in/hamza-el-massoudi-29a558235/}{\faLinkedin\ linkedin.com/in/hamza-el-massoudi-29a558235} \quad
    \href{https://github.com/ygwoah/}{\faGithub\ github.com/ygwoah}
\end{center}
\vspace{-4pt}
\hrule
\vspace{8pt}

% --------------------------------------------------
% Summary
% --------------------------------------------------
\section*{Summary}
Full-stack engineer specialized in distributed search systems (Oracle Cloud Infrastructure). Delivered 35\% faster CI pipelines and robust plugin-test coverage for OpenSearch. Adept at building scalable web/mobile apps and integrating AI-powered solutions using React, Spring Boot, PostgreSQL, and Docker.

% --------------------------------------------------
% Education
% --------------------------------------------------
\section{EDUCATION}

\begin{tabularx}{\linewidth}{@{}p{0.78\linewidth} r@{}}
	\textbf{Engineering Degree, Software Engineering \& Distributed Systems} — Ecole Normale Supérieure de l’Enseignement Technique, Mohammedia & 2022--2025 \\
	\textbf{B.Sc. Mathematics \& Computer Science} — Faculty of Science and Technology, Al Hoceima & 2021--2022 \\
	\textbf{DEUST} (Scientific and Technical University Studies) — Faculty of Science and Technology, Al Hoceima & 2019--2021 \\
\end{tabularx}

% --------------------------------------------------
% Experience
% --------------------------------------------------
\section{EXPERIENCE}

		\textbf{Software Engineer — Oracle}
\hfill Oct 2025--Present\\
	Casablanca, Morocco
\begin{itemize}[leftmargin=*]
    \item Designed retrieval-augmented generation (RAG) pipelines in Python to enrich search relevance and response quality.
    \item Built and deployed AI features for the product, leading efforts on prompt design, evaluation, and automation.
    \item Partnered with the team to propose and deliver roadmap improvements, accelerating experimentation and delivery cadence.
\end{itemize}

	\textbf{Software Engineer Intern — Oracle, OCI Search with OpenSearch}
\hfill Feb 2025--Aug 2025\\
Casablanca, Morocco
\begin{itemize}[leftmargin=*]
    \item Optimized CI pipeline, reducing test-suite time.
    \item Engineered plugin-test suite for OpenSearch using Java and Bash.
    \item Improved the observability of the testing.
\end{itemize}

	\textbf{Software Engineering Intern — FeverToken}
\hfill Jun 2023--Aug 2023\\
Remote, Paris, France
\begin{itemize}[leftmargin=*]
    \item Developed a mobile app as a crypto wallet.
    \item Implemented features for securing the wallet, including encryption and authentication.
    \item Added functionality for transferring money with blockchain integration.
\end{itemize}

% --------------------------------------------------
% Projects
% --------------------------------------------------
\section{PROJECTS}

	\textbf{Student Engagement \& Academic Management Platform (Freelance -- Contract)}
\hfill Sep 2024--Dec 2024 \\
Freelance
\begin{itemize}[leftmargin=*]
    \item Architected and delivered a scalable React Native app for 1,000+ concurrent students, enabling self-service, community engagement, and mentor matching.
    \item Integrated an AI-powered chatbot to automate and resolve student FAQs instantly.
    \item Engineered the platform using React Native, Node.js/Express, PostgreSQL, Firebase, and OpenAI API.
\end{itemize}

	\textbf{Survey Creation Platform}
\hfill 2024 \\
Personal Project
\begin{itemize}[leftmargin=*]
    \item Conceived and engineered a full-stack web platform for creating, distributing, and analyzing surveys.
    \item Implemented RESTful APIs and core business logic with \textbf{Spring Boot}, reducing survey creation time by 30\%.
    \item Crafted an intuitive, responsive frontend in \textbf{React} for seamless survey creation and real-time results visualization.
    \item Leveraged \textbf{PostgreSQL} for secure, scalable data management.
    \item Integrated user authentication and dynamic analytics to enhance user experience.
\end{itemize}

% --------------------------------------------------
% Skills
% --------------------------------------------------
\section{SKILLS}

	\textbf{Programming Languages}: TypeScript, JavaScript, Java \\
	\textbf{Frontend}: React, React Native, Next.js, Tailwind CSS \\
	\textbf{Backend}: Spring Boot, Express.js, Node.js \\
	\textbf{Databases}: MySQL, PostgreSQL, MongoDB, Firestore \\
	\textbf{Cloud}: Kubernetes, Terraform, Docker, Git, Linux, OCI

% --------------------------------------------------
% Languages & Interests
% --------------------------------------------------
\section{LANGUAGES \& INTERESTS}

	\textbf{Languages}: Arabic (Native), English (Fluent), French (Fluent) \\
	\textbf{Interests}: Football, Reading, Competitive Programming

\end{document}