\documentclass{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Define signature and address in the preamble for robust compilation.
\signature{Hamza EL MASSOUDI}
\address{Hamza EL MASSOUDI \\ Casablanca Morocco \\ +212 697 56 68 01 \\ hamza.elmassoudi.dev@gmail.com \\ linkedin.com/in/hamza-el-massoudi-29a558235 \\ github.com/ygwoah}

\begin{document}

\begin{letter}{Hiring Manager \\ AVL Maroc SARL AU \\ Direction des Ressources Humaines \\ Casablanca, Morocco}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the Full-Stack Java Developer position at AVL Maroc SARL AU. With over three years of professional experience in Java and Spring Boot backend development, complemented by hands-on front-end work in React and TypeScript, I am confident I can contribute to your teams building scalable, secure, and maintainable applications.

In my recent roles, I designed RESTful microservices with Spring Boot, integrated databases via JPA/Hibernate, and automated delivery with Docker and GitLab CI. On the front end, I built responsive React.js interfaces with TypeScript, using Redux for state management.

I contribute to microservices projects, write tests (JUnit, Jest), and handle CI/CD with Azure deployment. I'm proficient in Maven, Gradle, and Kubernetes.

What attracts me to AVL Maroc SARL AU is your commitment to technical excellence and mobility projects. My skills in Java/Spring, React, and DevOps, plus my analytical mindset and team collaboration, make me a good match.

I would welcome the opportunity to discuss how my background can help AVL deliver high-quality software. Thank you for considering my application.

\closing{Sincerely,}

\end{letter}

\end{document}