\documentclass[9pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{array}
\usepackage{tabularx}

% PDF metadata
\hypersetup{
    pdftitle={Hamza EL MASSOUDI Mobile Resume},
    pdfauthor={Hamza EL MASSOUDI},
    colorlinks=true,
    urlcolor=blue
}

% --------------------------------------------------
% Page layout
% --------------------------------------------------
\geometry{
    top    = 0.2in,
    bottom = 0.2in,
    left   = 0.4in,
    right  = 0.4in
}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\pagenumbering{gobble}

% --------------------------------------------------
% Section formatting
% --------------------------------------------------
\titleformat{\section}{\bfseries\large\raggedright}{}{0pt}{}
\titlespacing*{\section}{0pt}{4pt}{2pt}

% --------------------------------------------------
% Document start
% --------------------------------------------------
\begin{document}

% --------------------------------------------------
% Header
% --------------------------------------------------
\begin{center}
    {\LARGE \textbf{Hamza EL MASSOUDI}}\\
    \smallskip
    Software Engineer \textbar\ Casablanca, Morocco\\
    \smallskip
    \faPhone\; +212 697 56 68 01 \quad
    \href{mailto:hamza.elmassoudi.dev@gmail.com}{hamza.elmassoudi.dev@gmail.com} \quad
    \href{https://www.linkedin.com/in/hamza-el-massoudi-29a558235/}{\faLinkedin\ linkedin.com/in/hamza-el-massoudi-29a558235} \quad
    \href{https://github.com/ygwoah/}{\faGithub\ github.com/ygwoah}
\end{center}
\vspace{-6pt}
\hrule
\vspace{6pt}

% --------------------------------------------------
% Summary
% --------------------------------------------------
\section*{Summary}
Software Engineer with expertise in cross-platform development using React Native. Built scalable mobile applications for 1,000+ users, integrating Firebase, real-time data sync, and secure authentication. Proficient in frontend and backend technologies for seamless mobile experiences.

% --------------------------------------------------
% Education
% --------------------------------------------------
\section{EDUCATION}

\begin{tabularx}{\linewidth}{@{}p{0.78\linewidth} r@{}}
	\textbf{Engineering Degree, Software Engineering \& Distributed Systems} — Ecole Normale Supérieure de l’Enseignement Technique, Mohammedia & 2022--2025 \\
	\textbf{B.Sc. Mathematics \& Computer Science} — Faculty of Science and Technology, Al Hoceima & 2021--2022 \\
	\textbf{DEUST} (Scientific and Technical University Studies) — Faculty of Science and Technology, Al Hoceima & 2019--2021 \\
\end{tabularx}

% --------------------------------------------------
% Experience
% --------------------------------------------------
\section{EXPERIENCE}

	\textbf{Software Engineer Intern — Oracle, OCI Search with OpenSearch}
\hfill Feb 2025--Aug 2025\\
Casablanca, Morocco
\begin{itemize}[leftmargin=*]
    \item Optimized CI pipeline, reducing test-suite time.
    \item Engineered plugin-test suite for OpenSearch using Java and Bash.
    \item Improved the observability of the testing.
\end{itemize}

	\textbf{Software Engineering Intern — FeverToken}
\hfill Jun 2023--Aug 2023\\
Remote
\begin{itemize}[leftmargin=*]
    \item Developed a mobile cryptocurrency wallet app using React Native, optimized for iOS and Android platforms.
    \item Implemented features for securing the wallet, including encryption and authentication.
    \item Added functionality for transferring money with blockchain integration, ensuring cross-device compatibility.
    \item Deployed the app to test environments, achieving seamless performance on mobile devices.
\end{itemize}

% --------------------------------------------------
% Projects
% --------------------------------------------------
\section{PROJECTS}

	\textbf{Student Engagement \& Academic Management Platform (Freelance -- Contract)}
\hfill Sep 2024--Dec 2024 \\
Freelance
\begin{itemize}[leftmargin=*]
    \item Architected and delivered a scalable React Native app for 1,000+ concurrent students, enabling self-service, community engagement, and mentor matching.
    \item Integrated an AI-powered chatbot to automate and resolve student FAQs instantly.
    \item Engineered the platform using React Native, Node.js/Express, PostgreSQL, and OpenAI API.
\end{itemize}

	\textbf{AI Assistant App for Elderly Care}
\hfill 2024 \\
Freelance
\begin{itemize}[leftmargin=*]
    \item Designed UI in Figma for a subscription-based AI assistant app for elderly users, enabling audio-only interactions with an AI agent powered by OpenAI.
    \item Implemented React Native front-end components, integrating features such as YouTube video search and playback, map search with route display, push notifications, and reminders integration with native calendar.
    \item Collaborated on GitHub repository to complete the app, adding talking animations and enhancing overall functionality for improved user accessibility.
\end{itemize}

% --------------------------------------------------
% Skills
% --------------------------------------------------
\section{SKILLS}

	\textbf{Mobile Development}: React Native, Swift, Expo, Firebase, Xcode, Android Studio \\
	\textbf{Programming Languages}: JavaScript, TypeScript, Swift, Java \\
	\textbf{Frontend}: React, Next.js, Tailwind CSS \\
	\textbf{Backend}: Node.js, Express.js \\
	\textbf{Databases}: MongoDB, Firestore \\
	\textbf{DevOps}: Docker, Git

% --------------------------------------------------
% Languages & Interests
% --------------------------------------------------
\section{LANGUAGES \& INTERESTS}

	\textbf{Languages}: Arabic (Native), English (Fluent), French (Fluent) \\
	\textbf{Interests}: Football, Reading, Competitive Programming

\end{document}